%!TEX root = mb.tex

\begin{abstract}

It is increasingly common for enterprises and other organizations to outsource network processing -- such as firewalling and caching -- to the cloud, just as they often outsource compute and storage.
However, this poses a threat to enterprise confidentiality because the cloud provider gains access to the organization's traffic.

We design and build \sys, the first system that enables a cloud provider to offer a wide range of middleboxes while maintaining client confidentiality. \sys encrypts the traffic that reaches the cloud and enables the cloud to process the  traffic {\em without decrypting it}.
\sys supports a wide-range of middleboxes such as firewalls, NATs, web proxies, load balancers, intrusion prevention systems, and data exfiltration systems. Our evaluation shows that \sys supports these applications with competitive performance: because \sys makes no modifications to the dataplane for most middleboxes, throughput at most middleboxes is unaffected by our changes.

{\bf TODOS.}
\begin{myitemize}
  \item Reorder rule encryption section.
  \item Move rules discussion to TM section.
  \item Middlebox design/impl section
  \item Add a BlindBox section to Related Work, discuss thoroughly.
  \item New graphs/numbers in Eval
  \item Uh, are those bandwidth numbers correct????
  \item Clean up related work, tighten/shorten as much as possible.
  \item There are gazillions of missing references and citations.
  \item VERY LAST: cut cut cut cut to length.
\end{myitemize}
\end{abstract}
